Thesis Project Proposal Meeting

### 2021-06-30 meeting materials/thesis meeting 9:21:20.Rmd
i don't even know what i've done...

\newpage

@@

```{r, echo=FALSE}
knitr::include_graphics("images/option1_projprop.png")
```

\newpage

**Option 2:** Look exclusively at diurnal fluctuations of 3 different environmental variables (temp, pH, salinity, DO, light, etc.) across all levels of organization

@@

```{r, echo=FALSE}
knitr::include_graphics("images/option2_projprop.png")
```

@@

Figure 1 in Kroeker et al 2020 somewhat addresses what I wanted to accomplish with an NMDS plot, but I think it is a good jumping off place for thinking about how to design search terms and contextualize environmental variability bodies of literature

@@

\newpage
# Next steps and questions 
* Is the world predicted to become more variable or more autocorrelated? 
    + And if the answer is both, how do they interact? 
    + Is it that while the world will become more like its surrounding conditions, those conditions will increase in amplitude or become more severe?
* How do I properly use ISI advanced searches to get narrower results?
* How do I accumulate the right amount of keywords to accomplish this?
* What is the right scope for the two proposed detailed questions for this thesis project?

>>>>

@@

**Option 2:** Look exclusively at diurnal fluctuations of 3 different environmental variables (temp, pH, salinity) across all levels of organization

@@

@@

Figure 1 somewhat addresses what I wanted to accomplish with an NMDS plot, but I think it a good jumping off place for thinking about how to design search terms and contextualize environmental variability bodies of literature

```{r, fig.width=5, fig.height=5, echo=FALSE}
knitr::include_graphics("images/kroeker_fig1.png")
```

@@

# Next steps and questions 
* Is the world predicted to become more variable or more autocorrelated? 
    + And if the answer is both, how do they interact? 
    + Is it that while the world will become more like its surrounding conditions, those conditions will increase in amplitude or become more severe?

* How do I properly use ISI advanced searches to get narrower results?
* How do I accumulate the right amount of keywords to accomplish this?
* What is the right scope for the two proposed detailed questions for this thesis project?

### 2021-06-30 meeting materials/thesis proposal .Rmd
i don't even know what i've done...

Current search term ideas:
* "environmental variability" AND ecology AND temperature (1,281 results)
* "environmental variability" AND ecology (4049 results)
* "environmental variability" AND rate AND ecology (1,062 results)
* "environmental variability" AND ecology AND organism (802 results)
* "environmental variability" AND ecology AND population (2,458 results)
* "environmental variability" AND ecology AND community (1,275 results)
* "environmental variation" AND ecology (4,983 results)

>>>>

### Current search term ideas:

* "environmental variability" AND ecology AND temperature (1,281 results)
* "environmental variability" AND ecology (4049 results)
* "environmental variability" AND rate AND ecology (1,062 results)
* "environmental variability" AND ecology AND organism (802 results)
* "environmental variability" AND ecology AND population (2,458 results)
* "environmental variability" AND ecology AND community (1,275 results)
* "environmental variation" AND ecology (4,983 results)
